---
title: "Analysis of relation between Stars rating vs. most relevant Attributes and n-grams (words) in Reviews filtered by State and Business Category."
author: "Jose Maria Vilaverde"
date: "November 22th 2015"
output: pdf_document
---

***

##Introduction

In order to get top rate as business in a city is analyzed Where have to be established my business, which services I need to offer, what positive review words I need to be associated to my business and what negative review words I need to avoid

To do that analysis is used as input Business Category and City. As output: Top Rate, Neighborhood, Services, Top-5 positive words to promote, Top-5 negative words to avoid.

For example, If I want to open a business for category "dentist" in Arizona, I need to know where is the best place to open the business, services that I have to give to my customers, like "credit card accepted", and identify most relevant positive review words that I need to get from my customers and negative review words for my business category in Arizona.

***

##Methods and Data

###Steps:

**ETL -> 1.Get_Data.R**

* Download data from https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/yelp_dataset_challenge_academic_dataset.zip and unzip it.
* Extract json information from files "business","checkin","tip","review" (Excluded "user", not relevant for my analysis)
* Store it into RDS file. Review is divided into files with 100.000 lines/file in order to make affordable the calculation for my computer. For review I obtained 16 files.
* Identify business per state.
* Filter files per business_id per State, create RDS files "checkin","tip","review" per State.

**Process -> 2.Proces Data.R**

* Use as input State and Business Category.

**List of States:**

```{r states, echo=FALSE, message=FALSE, results='asis'}
source('2.Process Data.R')
#Get States
list_states <- list.files(dir_states)
list_states <- list_states[!grepl("resources",list_states)]
print(paste(list_states, collapse = ", "))
```

**List of Categories:**

```{r categories, echo=FALSE, message=FALSE, results='asis'}
state_filter <- "NC"

#Get an order list of categories
categories <- sort(categories()$getUniqueCategories(state_filter = state_filter)$categories)

print(paste(sort(categories), collapse = ", "))

```

* Intermediate Output to support analysis and define model
* Relation Attributes-Stars
* Count words.

Output

* Attributes to have, top-5 positive words (>=4 stars comments), top-5 negatives words (<3 stars comments).
* Map of top rated business.
* Random forest model fitted for a Business Category and State and analysis to verify that all those attributes and words have a correlation with star rates.

***

##Results - Describe what you found through your analysis of the data.

* Use as State: "NC" and "Food" as category.

**List of top attributes and Top-5 positive and negative words for 1-gram:**

List filtered, % of positive and negative over total must be over 2.5%, difference between positive and negative must be over 0.15 stars to be relevant.

```{r topAttributes, echo=FALSE, message=FALSE, results='asis'}
source('2.Process Data.R')
state_filter <- "NC"
category_filter <- "Food"

#% of positive and negative over total must be over 2.5%
validity_range <- 2.5

#Difference between positive and negative must be over 0.15 stars to be relevant
validity_difference <- 0.15

mainDataController <- data()

attTable <- mainDataController$getTotalsAttStars(overwrite = FALSE, state_filter = state_filter, category = category_filter)

library(dplyr)
attTable %>%
filter(state==state_filter, positive.over.total>validity_range, negative.over.total>validity_range,
                                      (difference_avg>validity_difference | difference_avg<(-validity_difference))) %>%
        select(-state) -> attTable

colnames(attTable) <- c("Attribute", "positives", "pos_avg", "negatives", "neg_avg", "diff_avg", "pos%", "neg%")

#Use library xtable to generate html table
library(xtable)
#xtable_attTable <- xtable(select(attTable, attribute, number_positive, positive_avg, number_negative, negative_avg, difference_avg, positive.over.total, 
xt_attTable <- xtable(attTable)

print(xt_attTable, include.rownames=FALSE, comment = FALSE)
```

```{r topWords, echo=FALSE, message=FALSE, results='asis'}
#source('2.Process Data.R')
#state_filter <- "NC"
#category_filter <- "Food"

mainTextAnalyst <- textAnalyst()

topTable <- mainTextAnalyst$getTopNGrams(stars_filter=c(4, 4.5, 5), state_filter=state_filter, category_filter = category_filter, top = 5)
xt_topTable <- xtable(topTable, caption = "Top-5 positive words")

bottomTable <- mainTextAnalyst$getTopNGrams(stars_filter=c(1, 1.5, 2, 2.5), state_filter=state_filter, category_filter = category_filter, top = 5)
xt_bottomTable <- xtable(bottomTable, caption = "Top-5 negative words")

print(xt_topTable, comment = FALSE)
print(xt_bottomTable, comment = FALSE)
```

------

**Map of Business:**

```{r mapBusiness, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}
mainData <- data()
mainCategories <- categories()

mapBusiness(state_filter = state_filter, category_filter = category_filter)
```

**Model:**

```{r model, echo=FALSE, message=FALSE, warning=FALSE}
mainModelController <- modelController()
mainModelController$init()
modelo <- mainModelController$createModelperState(recalculate = TRUE, state_filter = default_state, category_filter = "Food")
print(modelo)

```

***

##Discussion - Explain how you interpret the results of your analysis and what the implications are for your question/problem.






```{r}

```


